NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-17 ms_nihao_budget.tex
expand the abstract by adding our finding

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas ($10^7$K$ <
  T$), inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes are missing baryons. The missing
    mass been relocated past 2 virial radii, and is dominated by cool gas.
   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with recent observational estimates.
\end{abstract}

@@

%% FIGURE 5
\begin{figure*}
\centerline{
  \psfig{figure=budget_inout.eps,width=1.0\textwidth}
}
\caption{Mass fraction of gas in four phases (relative to the fiducial
  baryonic mass within the virial radius)
  {\bf gas inside the virial radius (filled blue points) and between 
   virial and baryon radius (open red points)}, respectively. Cool gas is
  the dominant component of {\bf the fiducial baryonic mass within the 
  virial radius for most galaxies ($10^{10} < M/\Msun < 10^{12}$, cold 
   and warm-hot gas is majority only for the galaxies at lower and higher
   mass end.}}
\label{fig:inout}
\end{figure*}

>>>>

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas (T$> 10^7$K) 
  , inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes are missing baryons. The missing
    mass been relocated past 2 virial radii, and {\bf cool gas dominates
  corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$) while the 
  warm-hot gas dominates dominates at high mass (M$_{200} \gta 3 \times 10^{11} \Msun$)}.
   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with recent observational estimates.
  {\bf Moreover, these more massive haloes reproduce the observed 
  fraction of cold, warm-hot and hot gas, the fraction of cool gas we
  predict is significant lower than the observation from COS-HALOs,
  but agree with the analysis of \citet{Stern16}}.
\end{abstract}

@@

%% FIGURE 5
\begin{figure*}
\centerline{
  \psfig{figure=budget_inout.eps,width=1.0\textwidth}
}
\caption{Mass fraction of gas in four phases (relative to the fiducial
  baryonic mass within the virial radius)
  {\bf gas inside the virial radius (filled blue points) and between 
   virial and baryon radius (open red points)}, respectively. Cool gas is
  the dominant component of {\bf the fiducial baryonic mass within the 
  virial radius for most galaxies ($10^{10} < M/\Msun < 10^{12}$), cold 
   and warm-hot gas is majority only for the galaxies at lower and higher
   mass end.}}
\label{fig:inout}
\end{figure*}
